---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sanssouci.data

<!-- badges: start -->
[![R-CMD-check](https://github.com/sanssouci-org/sanssouci.data/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/sanssouci-org/sanssouci.data/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of sanssouci.data is to provide data sets for the [sanssouci](https://github.com/sanssouci-org/sanssouci) package.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sanssouci-org/sanssouci.data")
```


## Data for differential gene expression studies (microarrays)

### Gene expression data set

```{r expr}
data(expr_ALL, package = "sanssouci.data")
str(expr_ALL)
```

This data set contains gene expression values for `r nrow(expr_ALL)` genes in `r ncol(expr_ALL)` cancer samples. These samples correspond to two types of Acute Lymphoblastic Leukemia (ALL):

```{r expr-samples}
table(colnames(expr_ALL))
```

This data set is used in the vignette [Permutation-based post hoc inference for differential gene expression studies](https://sanssouci-org.github.io/sanssouci/articles/post-hoc_differential-expression.html) of the [sanssouci](https://github.com/sanssouci-org/sanssouci) package.

### Gene Ontology (BP)

```{r GO-BP}
data(hgu95av2_GO_BP, package = "sanssouci.data")
str(hgu95av2_GO_BP)
```

This data set contains all `r ncol(hgu95av2_GO_BP)` Gene Ontology (GO) terms from the Biological Process (BP) ontology. Non-zero entries in column 'c' indicate the genes corresponding to the 'c'-th GO term. The GO ids are stored in the column names of the matrix.  

### Gene Ontology (for a subset of genes)

```{r GO}
data("expr_ALL_GO", package = "sanssouci.data")
str(expr_ALL_GO)
```

This data set contains `r ncol(expr_ALL_GO)` Gene Ontology (GO) terms (not only from the BP ontology). Non-zero entries in column 'c' indicate the genes corresponding to the 'c'-th GO term. The GO ids are stored in the column names of the matrix.  

These GO terms are those containing at least an entry whose associated $p$-value of the test of differential expression in the `expr_ALL` data set is less than 0.0001.

### Genome positions

```{r probe-annotation}
data("expr_ALL_annotation", package = "sanssouci.data")
head(expr_ALL_annotation)
```
This data set contains the chromosome, start and end position of each of the genes in the `expr_ALL` data set.

## Data for differential gene expression studies (RNA sequencing)

### Gene expression data set

```{r RNAseq}
data("RNAseq_blca", package = "sanssouci.data")
str(RNAseq_blca)
```


This data set contains gene expression values for `r nrow(RNAseq_blca)` genes in `r ncol(RNAseq_blca)` cancer samples. These samples correspond to urothelial bladder cancer samples with two different stages:

```{r RNAseq-samples}
table(colnames(RNAseq_blca))
```

### Gene Ontology (for a subset of genes)

```{r GO-RNAseq}
data("RNAseq_blca_GO", package = "sanssouci.data")
str(RNAseq_blca_GO)
```

This data set contains `r ncol(RNAseq_blca_GO)` Gene Ontology (GO) terms. Non-zero entries in column 'c' indicate the genes corresponding to the 'c'-th GO term. The GO ids are stored in the column names of the matrix.  

These GO terms are those containing at least an entry whose associated $p$-value of the test of differential expression in the `RNAseq_blca` data set is less than 0.0001.


## Neuroimaging data set


```{r fMRI}
data("fMRI_localizer", package = "sanssouci.data")
str(fMRI_localizer)
```

This data set contains Functional Magnetic Resonance Imaging (fMRI) measurements corresponding to two motor tasks from the Localizer data set: "left click" and "right click":

```{r fMRI-samples}
table(colnames(fMRI_localizer))
```

This data set is used in the vignette [Permutation-based post hoc inference for fMRI studies](https://sanssouci-org.github.io/sanssouci/articles/post-hoc_fMRI.html) of the [sanssouci](https://github.com/sanssouci-org/sanssouci) package.
