---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sansSouci.data

<!-- badges: start -->
[![R build status](https://github.com/pneuvial/sanssouci.data/workflows/R-CMD-check/badge.svg)](https://github.com/pneuvial/sanssouci.data/actions)
<!-- badges: end -->

The goal of sansSouci.data is to provide data sets for the [sansSouci](https://github.com/pneuvial/sanssouci) package.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pneuvial/sanssouci.data")
```


## Data for differential gene expression studies (microarrays)

### Gene expression data set

```{r expr}
data(expr_ALL, package = "sansSouci.data")
str(expr_ALL)
```

This data set contains gene expression values for `r nrow(expr_ALL)` genes in `r ncol(expr_ALL)` cancer samples. These samples correspond to two types of Acute Lymphoblastic Leukemia (ALL):

```{r expr-samples}
table(colnames(expr_ALL))
```

This data set is used in the vignette [Permutation-based post hoc inference for differential gene expression studies](https://pneuvial.github.io/sanssouci/articles/post-hoc_differential-expression.html) of the [sansSouci](https://github.com/pneuvial/sanssouci) package.

### Gene annotation

```{r GO}
data(hgu95av2_GO_BP, package = "sansSouci.data")
str(hgu95av2_GO_BP)
```

This data set contains `r ncol(hgu95av2_GO_BP)` Gene Ontology (GO) terms from the Biological Process (BP) ontology. Non-zero entries in column 'c' indicate the probes corresponding to the 'c'-th GO term. The GO ids are stored in the column names of the matrix.  

These GO terms are those containing at least an entry whose associated $p$-value of the test of differential expression in the `expr_ALL` data set is less than 0.00001.

## Data for differential gene expression studies (RNA sequencing)

### Gene expression data set

```{r RNAseq}
data("RNAseq_blca", package = "sansSouci.data")
str(RNAseq_blca)
```


This data set contains gene expression values for `r nrow(RNAseq_blca)` genes in `r ncol(RNAseq_blca)` cancer samples. These samples correspond to urothelial bladder cancer samples with two different stages:

```{r RNAseq-samples}
table(colnames(RNAseq_blca))
```


## Neuroimaging data set


```{r fMRI}
data("fMRI_localizer", package = "sansSouci.data")
str(fMRI_localizer)
```

This data set contains Functional Magnetic Resonance Imaging (fMRI) measurements corresponding to two motor tasks from the Localizer data set: "left click" and "right click":

```{r fMRI-samples}
table(colnames(fMRI_localizer))
```

This data set is used in the vignette [Permutation-based post hoc inference for fMRI studies](https://pneuvial.github.io/sanssouci/articles/post-hoc_fMRI.html) of the [sansSouci](https://github.com/pneuvial/sanssouci) package.
